---
title: "Web Scraping - Coinmarketcap.com Data"
output: rmarkdown::github_document
---

This repo contains a set of functions that can be used to scrape historical cryptocurrency market data from [coinmarketcap.com](https://coinmarketcap.com "coinmarketcap"):

- ```GetTotalCryptoCurrencyMarketCapitalization``` - Fetch Cryptocurrency market capitalization data (total, bitcoin, alts).
- ```GetAllExistingTickers``` - Fetch all available cryptocurrency tickers & symbol-id's over a given time period.
- ```GetHistoricalTimeseriesDataForTickers``` - Fetch weekly timeseries data for a set of tickers over a given time period.
- ```GetHistoricalTopPerformingCoins``` - Fetch market-cap rankings of top performing coins over a given time period.

# Examples

### GetTotalCryptoCurrencyMarketCapitalization

```{r message=FALSE}
source("config/Config.R")
first.date <- as.POSIXct("2013-04-28", format="%Y-%m-%d", tz="UTC")
last.date  <- as.POSIXct(Sys.Date() - lubridate::days(1), format="%Y-%m-%d", tz="UTC")

# Scraping coinmarketcap
# historical.market.cap <- GetTotalCryptocurrencyMarketCapitalization(first.date = first.date,
#                                                                     last.date  = last.date,
#                                                                     save.data  = TRUE)

## Loading the data from previously saved .rds file in ./data directory
historical.market.cap <- GetTotalCryptocurrencyMarketCapitalization(load.data = TRUE)


PlotChart <- function(chart.data, zoom="2016/2017", name=NULL){
  chart.alts <- chartSeries(chart.data, 
                            TA   = 'addEMA(n=10, col="yellow");addEMA(n=30, col="red");addMACD()', 
                            name = name, 
                            plot=FALSE)
  zoomChart(zoom)
}

PlotChart(historical.market.cap$alts, zoom="2016/2017", name = "Weekly Altcoin Market Cap")
```

### GetAllExistingTickers

```{r message=FALSE}
# Scraping from coinmarketcap.com
# all.historical.tickers <- GetAllExistingTickers(first.date = first.date,
#                                                 last.date  = last.date,
#                                                 save.data  = TRUE)

# Loading the data from previously saved .rds file in ./data directory
all.historical.tickers <- GetAllExistingTickers(load.data = TRUE)

# Show amount of unique tickers
length(all.historical.tickers)
# Show first 100
head(all.historical.tickers, 100)

## Todo: In some cases, there exist multiple tickers for the same ticker-id.
## XLM/STR | LSK/LISK | ANS/NEO | there could potentially be others. (to fix..)
stellar <- "XLM"; names(stellar) <- "id-stellar"
lisk    <- "LSK"; names(lisk)    <- "id-lisk"
neo     <- "NEO"; names(neo)     <- "id-neo"
all.historical.tickers <- c(all.historical.tickers, stellar, lisk, neo)
```

### GetHistoricalTimeseriesDataForTickers

```{r message=FALSE}
# Scraping from coinmarketcap.com
# historical.crypto.series <- GetHistoricalTimeseriesDataForTickers(tickers    = all.historical.tickers,
#                                                                   first.date = first.date,
#                                                                   last.date  = last.date,
#                                                                   save.data  = TRUE)

historical.crypto.series <- GetHistoricalTimeseriesDataForTickers(load.data = TRUE)
dim(historical.crypto.series)

# plot random selection of coin graphs
# note: make sure that data is available for the plotted serires
head(historical.crypto.series[, 1:10])
tail(historical.crypto.series[, 1:10])
chart.it <- sapply(2:9, function(x) PlotChart(historical.crypto.series[,x],
                                              name = names(historical.crypto.series[,x])))

########
## todo: In some cases, There exist multiple ticker-id's for the same ticker symbol
## ex, ETC corresponds to'id-ethercoin' and 'id-ethereum-classic'
# There could potentially be others as well (to fix)
# etc.tickers        <- "ETC"
# names(etc.tickers) <- "id-ethereum-classic"
# etc <- GetWeeklyTimeseriesDataForTickers(tickers    = etc.tickers,
#                                          first.date = first.date,
#                                          last.date  = last.date)
# # add id-ethereum-classic
# historical.crypto.series <- cbind(historical.crypto.series, etc)
```

### GetHistoricalTopPerformingCoins

```{r message=FALSE}
# Scraping from coinmarketcap.com
# nr.top.coins = 10
# historical.top.coins <- GetHistoricalTopPerformingCoins(nr.top.coins = 10,
#                                                         first.date   = first.date,
#                                                         last.date    = last.date,
#                                                         save.data    = TRUE)

historical.top.coins <- GetHistoricalTopPerformingCoins(load.data = TRUE)

head(historical.top.coins)
tail(historical.top.coins)
```

## Donations

If you find this software useful and/or you would like to see additional extensions, feel free to donate some crypto:

 - BTC: 1QHtZLZ15Cmj4FPr5h5exDjYciBDhh7mzA
 - LTC: LhKf6MQ7LY1k8YMaAq9z3APz8kVyFX3L2M
 - ETH: 0x8E44D7C96896f2e0Cd5a6CC1A2e6a3716B85B479
 - DASH: Xvicgp3ga3sczHtLqt3ekt7fQ62G9KaKNB

Or preferably, donate some of my favorite coins :)

 - GAME: GMxcsDAaHCBkLnN42Fs9Dy1fpDiLNxSKX1
 - WAVES: 3PQ8KFdw2nWxQATsXQj8NJvSa1VhBcKePaf
 
## Licensing

Copyright 2017 Essential Data Science Consulting ltd. ([EssentialQuant.com](http://essentialquant.com "EssentialQuant") / jellenvermeir@essentialquant.com).
This software is copyrighted under the MIT license: View added [LICENSE](./LICENSE) file.
